Draft Research pt1

### 2019-03-04 draftResearch_pt1.Rmd
mini eureka moment extracting player data from JSON response
Updated API interaction for coercing data to df, iterating for multiple pages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/yahoo_api.R")
library(tidyverse)
```

# Position Eligibility

```{r}
get_json("users;use_login=1/games;game_keys=mlb/players;start=0") %>% 
  content() -> players_resp

players_resp$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_list

players_list %>% saveRDS("data/players_list.Rds")

players_list$count -> row_count

players_list$`0`[[1]][[1]] %>% flatten() %>% as.data.frame() -> ex_data

suppressWarnings(
  lapply(players_list[1:25], function(x) x[[1]][[1]] %>% 
           flatten() %>% 
           as.data.frame()) %>% 
    bind_rows() %>% 
    as_tibble() %>%
    select(-(14:16))-> raw_df
)
```
So this is a list of 26 elements, 25 lists, and "count" int = 25. One player is represented in each of the 25 nested lists, but their data is actually three levels of nesting beneath!

Wrote a function to get iteratively get 25 players, get their data into a df and bind together:

```{r}
(get_players(50) -> tst_results)

```

Next, test and cleanup the data, specifically getting the position eligibility. Add a sleep time between calls so we don't hit the API over and over. See if we can join it with the Fangraphs data. Bonus points for applying other pipe operators.

# Projection Data
